Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-03-12 manuscript/manuscript.Rmd
added model validation section

We used random draws from the final 1,000 iterations from each of three MCMC chains to introduce stochasticity into our population models. At each time step, we first randomly selected climate covariates from one of the 14 observed years and also randomly drew one set of random year effects for each vital rate regression. Climate years and random year effects were drawn independently because they were uncorrelated. Then, we drew the full parameter set (specific random year effects, climate effects, fixed effects) from a randomly selected MCMC iteration. We selected random year effects and the climate year independently.

Results
-------

>>>>

We used random draws from the final 1,000 iterations from each of three MCMC chains to introduce stochasticity into our population models. At each time step, we randomly selected climate covariates from one of the 14 observed years. Then, we drew the full parameter set (climate effects and density-dependence fixed effects) from a randomly selected MCMC iteration. Since our focus was on the contribution of climate covariates to population states, we set the random year effects and the random group effects to zero.

### Model validation
To test each model's ability to forecast the population state we used leave-one-year-out cross validation. For both levels of modeling, we fit the vital rate models using observations from all years except one, and then used those fitted parameters in the population models to perform a one-step-ahead forecast for the year whose observations were withheld from model fitting. We repeated this procedure for all 13 observation years. This model validation allowed us to compare accuracy and precision of the two modeling approaches (individual-level versus population-level).

Results
-------
### Vital rate statistical models

### Model validation

### Climate change simulations

### 2015-03-12 manuscript/manuscript.tex
added model validation section

We used random draws from the final 1,000 iterations from each of three
MCMC chains to introduce stochasticity into our population models. At
each time step, we first randomly selected climate covariates from one
of the 14 observed years and also randomly drew one set of random year
effects for each vital rate regression. Climate years and random year
effects were drawn independently because they were uncorrelated. Then,
we drew the full parameter set (specific random year effects, climate
effects, fixed effects) from a randomly selected MCMC iteration. We
selected random year effects and the climate year independently.

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{One step forecasts from IPM version.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3.pdf}
\caption{One step forecasts from IPM version.}
\end{figure}

>>>>

We used random draws from the final 1,000 iterations from each of three
MCMC chains to introduce stochasticity into our population models. At
each time step, we randomly selected climate covariates from one of the
14 observed years. Then, we drew the full parameter set (climate effects
and density-dependence fixed effects) from a randomly selected MCMC
iteration. Since our focus was on the contribution of climate covariates
to population states, we set the random year effects and the random
group effects to zero.

\subsubsection{Model validation}\label{model-validation}

To test each model's ability to forecast the population state we used
leave-one-year-out cross validation. For both levels of modeling, we fit
the vital rate models using observations from all years except one, and
then used those fitted parameters in the population models to perform a
one-step-ahead forecast for the year whose observations were withheld
from model fitting. We repeated this procedure for all 13 observation
years. This model validation allowed us to compare accuracy and
precision of the two modeling approaches (individual-level versus
population-level).

@@

\subsubsection{Vital rate statistical
models}\label{vital-rate-statistical-models}

\subsubsection{Model validation}\label{model-validation-1}

\subsubsection{Climate change
simulations}\label{climate-change-simulations}

@@

\includegraphics{components/figure/manuscript-figure_21.pdf}
\includegraphics{components/figure/manuscript-figure_22.pdf}
